\documentclass[8pt,letterpaper]{article}

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1
\input{glyphtounicode}

% ===== One-page, ATS-safe, keeps full content =====
\usepackage[margin=0.45in, top=0.42in, bottom=0.44in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage{ragged2e}

\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}
\pagestyle{empty}

\linespread{0.95}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\tabcolsep}{4pt}

% Section style
\titleformat{\section}{\bfseries\normalsize}{}{0pt}{}[\vspace{2pt}\titlerule]
\titlespacing{\section}{0pt}{4pt}{2pt}

% Bullet & list spacing - adjusted for a clean, single-page fit
\setlist[itemize]{itemsep=-1pt, topsep=1.5pt, parsep=0pt, partopsep=0pt, leftmargin=10pt, label=\textbullet}

% Consistent left-aligned dates (same start position)
\newcommand{\daterow}[2]{%
  \noindent\begin{tabularx}{\textwidth}{@{}X >{\raggedright\arraybackslash}p{3.6cm}@{}}%
  \textbf{#1} & \emph{#2}\\
  \end{tabularx}%
}

\begin{document}

% =================== HEADER ===================
\begin{center}
{\Large \textbf{Ankit Prajapat}}\\[-1pt]
\href{mailto:akprajapat1824@gmail.com}{akprajapat1824@gmail.com} \,|\, 
\href{https://www.linkedin.com/in/ankit-prajapat/}{www.linkedin.com/in/ankit-prajapat/} \,|\, 
\href{https://github.com/ankit1824}{github.com/ankit1824}\\[0pt]
+91 9893782908 \,|\, Indore, MP
\end{center}

% =================== EDUCATION ===================
\section{Education}

\daterow{Maulana Azad National Institute of Technology -- Bhopal}{Aug 2023 -- Jun 2027}\\[-2pt]
Bachelor of Technology in Electronics and Communication Engineering $|$ CGPA: \textbf{8.85}\\[2pt]
\noindent\begin{tabularx}{\textwidth}{@{}X >{\raggedright\arraybackslash}p{3.6cm}@{}}%
Minor Specialization in Computer Science Engineering & \emph{Jul 2024 -- Jun 2027}\\%
\end{tabularx}\\[4pt]
\daterow{Excellent Academy (MP Board) -- Indore, MP}{Apr 2021 -- Apr 2022}\\[-2pt]
Class 12th $|$ Percentage: \textbf{87.6\%}

% =================== TECHNICAL SKILLS ===================
\section{Technical Skills}

\begin{tabularx}{\textwidth}{@{}>{\bfseries}l X@{}}
Languages & C, C++, SQL, JavaScript, Python \\

Frontend Technologies & React.js, Redux Toolkit, TypeScript, HTML, CSS, Tailwind CSS, Bootstrap \\

Backend \& Databases & Node.js, Express.js, FastAPI, REST APIs, MongoDB, MySQL, JWT \\

CS Fundamentals & Object-Oriented Programming (OOPs), DBMS, Operating Systems, Machine Learning \\

Tools \& Platforms & Git, GitHub, VS Code, Cursor, Jupyter Notebook, Vercel, Render \\
\end{tabularx}

% =================== PROJECTS ===================
\section{Projects} 

\textbf{TeamMatch AI -- ML Teammate Matcher \& Analyzer} \hfill \href{https://github.com/ankit1824/TeamMatch-AI}{GitHub} $|$ \href{https://team-match-ai-xi.vercel.app/}{Live}\\
Developed a full-stack teammate matchmaking and grouping platform using \textbf{React}, \textbf{FastAPI}, and \textbf{SQLite} to assemble balanced project teams. Engineered a \textbf{complementary recommendation engine} using \textbf{K-Nearest Neighbors (KNN)} on an 8D normalized profile vector space utilizing Cosine Distance metrics on inverted skills. Built a team diagnostics pipeline using \textbf{K-Means Clustering} for developer archetype categorization and computed a \textbf{Role Diversity Score}.

\vspace{3pt}

\textbf{AI Course Architect -- Personalized Learning Platform} \hfill \href{https://github.com/ankit1824/AI-Course-Architect}{GitHub} $|$ \href{https://skillsurgefinal.vercel.app/}{Live}\\
Built an AI-powered learning platform using \textbf{React}, \textbf{TypeScript}, and the \textbf{Google Gemini API} to generate \textbf{personalized course roadmaps}. Implemented \textbf{dynamic content rendering} with \textbf{React Markdown} and designed a responsive UI using \textbf{Tailwind CSS}.

\vspace{3pt}

\textbf{E-commerce Database System (SQL)} \hfill \href{https://github.com/ankit1824/E-commerce-DB}{GitHub}\\
Designed a \textbf{normalized MySQL database} (15+ tables) using \textbf{ER modeling}, \textbf{primary/foreign keys}, and \textbf{many-to-many relationships}. Wrote complex \textbf{SQL queries} with \textbf{JOINs}, \textbf{aggregations}, and \textbf{subqueries} for order tracking and analytics.

% =================== POR ===================
\section{Positions of Responsibility}

\textbf{Senior Executive, Robotics Club -- MANIT} \hfill \textit{May 2024 -- Present}
\begin{itemize}
    \item Co-organized flagship technical events (Automax, Makeathon, Roborace) attracting \textbf{500+} participants, managing cross-team coordination and event logistics.
    \item Led technical demonstrations of microcontrollers and sensor integration (Arduino, ESP32) for \textbf{50+} first-year students, fostering hands-on learning.
    \item Supported arena hardware configurations, signal checking, and diagnostic troubleshooting for competition systems.
\end{itemize}
\vspace{2.5pt}
\textbf{Member, Training and Placement Cell -- MANIT} \hfill \textit{Feb 2026 -- Present}
\begin{itemize}
    \item Researched and compiled a database of \textbf{200+} corporate HR contacts from LinkedIn to streamline outreach for student internships and full-time drives.
    \item Managed logistics and registration coordination for \textbf{300+} students during online assessments, scheduling, and interview shortlists.
    \item Facilitated communication of timelines and policy compliance to students, ensuring high participation rates during the placement season.
\end{itemize}
\vspace{2.5pt}
\textbf{Class Representative, ECE Department -- MANIT} \hfill \textit{Aug 2024 -- May 2025}
\begin{itemize}
    \item Represented a cohort of \textbf{80+} ECE students, serving as the primary liaison to faculty and administration for academic coordination.
    \item Streamlined academic communications (timetables, exam schedules, assignments) using digital channels to ensure timely student responses.
    \item Consolidated student feedback on course pace and curriculum to resolve academic disputes and align educational goals.
\end{itemize}

% =================== ACHIEVEMENTS ===================
\section{Achievements}
\vspace{2.5pt}
\begin{itemize}[itemsep=2.5pt]
  \item Solved \textbf{600+} Data Structures and Algorithms (DSA) problems, strengthening expertise in dynamic programming, graphs, trees, and greedy algorithms.
  \item Competitive Programming Ratings: 
  \href{https://leetcode.com/u/ankitp_18/}{LeetCode} (Peak Rating: \textbf{2007}, Knight), 
  \href{https://www.codechef.com/users/ankitp_18}{CodeChef} (Peak Rating: \textbf{1823}, 4-Star), and 
  \href{https://codeforces.com/profile/Ankit_Prajapat}{Codeforces} (Peak Rating: \textbf{1567}, Specialist).
  \item Secured a \textbf{Top 3} rank at Kriyeta 4.0, a state-level hackathon held at AITR, Indore, competing against 50+ teams.
\end{itemize}

\end{document}
